Density estimations for dispersal kernels

### 2016-10-10 Data/kernels.Rmd
Edited adehabitatHS code for dist.

---
title: "Density estimations for dispersal kernels"
author: "Pedro Jordano"
date: "enero 29, 2015"
output: html_document
bibliography: refs.bib
---

@@

```{r levy, fig.height=5, fig.width=8}
# Lévy distribution. -----------------------------------------------------
# dd<- abs(rnorm(1000, mean = 32.7, sd = 415)) # Normal distrib.
# dd<- rweibull(1000, shape= 1, scale = 3.5)   # Weibull distrib.
# dd<- rgamma(1000, scale= 100, shape= 10)     # Gamma distrib.
                                               # req. adehabitatHS
dd<- as.data.frame(simm.levy(1:1000, mu = 1.5, burst = "mu = 1.5")) 
dd<- na.omit(dd$dist)

>>>>

---
title: "Density estimations for dispersal kernels"
author: "Pedro Jordano"
date: "enero 29, 2015"
output: html_notebook
#bibliography: refs.bib
---

@@

```{r levy, fig.height=5, fig.width=8}
# Lévy distribution. -----------------------------------------------------
# dd<- abs(rnorm(1000, mean = 32.7, sd = 415)) # Normal distrib.
# dd<- rweibull(1000, shape= 1, scale = 3.5)   # Weibull distrib.
# dd<- rgamma(1000, scale= 100, shape= 10)     # Gamma distrib.
                                               # req. adehabitatHS
library(adehabitatHS)
dd<- simm.levy(1:1000, mu = 1.5, burst = "mu = 1.5")
dd<- na.omit(dd[[1]]$dist)
